---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mediacloudr

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Build Status](https://travis-ci.org/jandix/mediacloudr.svg?branch=master)](https://travis-ci.org/jandix/mediacloudr)
<!-- badges: end -->

The goal of mediacloudr is to provide a consistent wrapper for the 
mediacloud.org API. The Media Cloud platform is an open-source platform, 
that collects all kind of news stories and provides various functionalities to 
query, download and analyse them. This packages tries to support R users by
providing a set of functions to access various functionalities of the 
mediacloud.org.

## Installation

<!-- You can install the released version of mediacloudr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("mediacloudr")
```
-->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jandix/mediacloudr")
```

## API key

Please [register](https://topics.mediacloud.org/#/user/signup)  as a new user. 
Afterwards, you can copy your API key from your 
[profile page](https://topics.mediacloud.org/#/user/profile).

I suggest to save the API key to your R environment file. The R environment file
is loaded everytime R is started/restarted. You should not add the key to your
scripts, because other users could misuse your key. The following steps show
how to add the key to your R environment file.

1. Open your .Renviron file. The file is usually located in 
your home directory. If the file does not exist, just create one and name it
`.Renviron`.
2. Add a new line and enter your API key in the following format: 
`MEDIACLOUD_API_KEY=<YOUR_API_KEY>`.
3. Save the file and restart your current R session to start using mediacloudr.

## Request Limits

The mediacloud.org states the following for API request/rate limits:

"Each user is limited to 1,000 API calls and 20,000 stories returned in any 7 
day period. Requests submitted beyond this limit will result in a status 403 
error. Users who need access to more requests should email 
[info@mediacloud.org](mailto:info@mediacloud.org)."

## Examples

### Get a news story by id

You can query news stories by their ids. The ids can be found using the 
graphical interface or using the `get_story_list` function.

*Note*: You don't have to add the `api_key` argument if you followed the 
steps to add the api key to your R environment file.

```{r story example, eval=FALSE}
story_id <- 27456565L
story <- get_story(story_id = story_id)
```

### Get a list with news stories

You can query a list of news stories using `get_story_list`. You can use the 
`q` and `fq` arguments to filter stories. A guide to the query parameters can 
be found [here](https://mediacloud.org/support/query-guide/).

*Note*: You don't have to add the `api_key` argument if you followed the 
steps to add the api key to your R environment file.

```{r story list example, eval=FALSE}
stories <- get_story_list(q = "trump")
```

